---
title: "Assignment11"
output: pdf_document
---

// Objective function 
// Each of the x is a set of days off starting with SundayMonday
// Each of the values is the cost per worker
min: 775x1 + 800x2 + 800x3 + 800x4 + 800x5 + 775x6 + 750x7;

// Constraints
// Each constraint is the combination of all shifts that could cover the days off excluding any which partially cover days off.

SundayMonday:      x3 + x4 + x5 + x6 >= 27;
MondayTuesday:     x4 + x5 + x6 + x7 >= 27;
TuesdayWednesday:  x1 + x5 + x6 + x7 >= 26;
WednesdayThursday: x1 + x2 + x6 + x7 >= 26;
ThursdayFriday:    x1 + x2 + x3 + x7 >= 25;
FridaySaturday:    x1 + x2 + x3 + x4 >= 21;
SaturdaySunday:    x2 + x3 + x4 + x5 >= 19;

int x1, x2, x3, x4, x5, x6, x7;

```{r}
library(lpSolveAPI)
x <- read.lp("assignment11-4.lp")
x
```

```{r}
solve(x)
get.objective(x)
get.variables(x)
```
The total cost is 33550 Dollars per week.

The number of workers each day meets the minimum. Each shift 1 -> 7 needs the following number of workers at a minimum 4, 2, 9, 6, 2, 10, 10.

This means that the two workers who are on shift 1 will work Tuesday -> Saturday and so on.

Total workers coming from each shift:
Sunday     0 2 9 6 2 10 0       
Monday     0 0 9 6 2 10 10           
Tuesday    4 0 0 6 2 10 10           
Wednesday  4 2 0 0 2 10 10           
Thursday   4 2 9 0 0 10 10           
Friday     4 2 9 6 0 0  10           
Saturday   4 2 9 6 2 0  0             


Totals: 
Sunday    - 29
Monday    - 37
Tuesday   - 32
Wednesday - 28
Thursday  - 35
Friday    - 31
Saturday  - 23
