---
title: "Ecurley1_Assignment 8"
output: pdf_document
---

```{r}
#install.packages("Benchmarking")
library(Benchmarking)
```

```{r}
x <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2.0,1.2,.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(y) <- c("3rd Party","Private")
colnames(x) <- c("Staff Hours","Supplies")
x
y
```
```{r}
e <- dea(x,y,RTS = "fdh")            # provide the input and output 
e
peers(e)                             # identify the peers
lambda(e)
```
```{r}
e <- dea(x,y,RTS = "crs")            # provide the input and output 
e
peers(e)                             # identify the peers
lambda(e)
```
```{r}
e <- dea(x,y,RTS = "vrs")            # provide the input and output 
e
peers(e)                             # identify the peers
lambda(e)
```

```{r}
e <- dea(x,y,RTS = "irs")            # provide the input and output 
e
peers(e)                             # identify the peers
lambda(e)
```
```{r}
e <- dea(x,y,RTS = "drs")            # provide the input and output 
e
peers(e)                             # identify the peers
lambda(e)
```
```{r}
e <- dea(x,y,RTS = "fdh+")            # provide the input and output 
e
peers(e)                             # identify the peers
lambda(e)
```


```{r}
x <- matrix(c(1,1,1,1,1,1,
         1.0000,1.0000,1.0000,1.0000,0.9775,0.8675,
         1.0000,1.0000,1.0000,1.0000,1.0000,0.8963,
         1.0000,1.0000,1.0000,1.0000,1.0000,0.8963,
         1.0000,1.0000,1.0000,1.0000,0.9775,0.8675,
         1,1,1,1,1,1
          ),ncol = 6)
colnames(x) <- c("FDH","CRS","VRS","IRS","DRS","FRH/FDH+")
x
```

We can see here that under the assumption of FDH and FHR all sites are preforming at peek efficiency
However when we consider other methods such as CRS VRS IRS and DRS we see that site 5 & 6 perform under peek efficiency. 

For example under CRS site 5 is %97.75 efficient, thus they should be able to improve their efficiency by mimicing the effort of their closest peers (Sites 1,2,&4)
This same process can be applied to the other methods and peers.

Under the assumption of CRS and DRS site 5 should mimic sites 1,2, & 4
Under the assumption of CRS and DRS site 6 should mimic sites 1,2, & 4
Under the assumption of VRS and IRS site 6 should mimic sites 1,2, & 5

The weights as indicated by the lambdas will indicate how important each of those sites should be weighted.


