---
title: "Ecurley_6"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
#install.packages("lpSolveAPI")
#tinytex::install_tinytex()
```
```{r}
library(lpSolveAPI)
```


We start with an LP model that has 6 variables. One for each of the costs associated with shipping between warehouses and factories. Then we indicated the costs (I started with Plant A, Then Plant B)

I added either 600 or 625 to each of the variables because that is the unit cost per item in Plant A and B Respectively

Next I added 2 additional variables as dumby variables. This is because the total demand from the warehouses is 210, yet the total supply is 220. I have to add a dumby warehouse to account for the difference.

I also set the cost of using this dumby variable to 0 since we don't know the shipping cost, only the production value.

Finally we indiacte that the overall function is going to be a minimization of the cost.
```{r}
lprec <- make.lp(0,8)
set.objfn(lprec, c(22+600, 14+600, 30+600, 0+600,
                   16+625, 20+625, 24+625, 0+625))
lp.control(lprec, sense='min')

```

Next I added two constraints. These constraints ensure that the production matches the production per plant.

```{r}
add.constraint(lprec, c(1,1,1,1,0,0,0,0), "=", 100)
add.constraint(lprec, c(0,0,0,0,1,1,1,1), "=", 120)
```

Then I added 4 constraints to meet the demand from the warehouses.

```{r}
add.constraint(lprec, c(1,0,0,0,1,0,0,0), "=", 80)
add.constraint(lprec, c(0,1,0,0,0,1,0,0), "=", 60)
add.constraint(lprec, c(0,0,1,0,0,0,1,0), "=", 70)
add.constraint(lprec, c(0,0,0,1,0,0,0,1), "=", 10)
```

Next I set the lower bound of all the constratints to 0

```{r}
set.bounds(lprec, lower = c(0,0,0,0,0,0,0,0), columns = c(1,2,3,4,5,6,7,8))
```

We can then set the names of the outputs
```{r}
Rownames <- c("Production Cap Plant A", "Production Cap Plant B", "Demand Warehouse 1", "Demand Warehouse 2", "Demand Warehouse 3", "Demand Warehouse 4")

ColNames <- c("PlantA->W1", "PlantA->W2", "PlantA->W3", "PlantA->W4",
              "PlantB->W1", "PlantB->W2", "PlantB->W3", "PlantB->W4")

dimnames(lprec) <- list(Rownames, ColNames)
```

```{r}
lprec
solve(lprec)

```

We can see that the minimum cost to ship is 138,980 and the number of items to be shipped to each warehouse.

Starting from Left to Right 
Plant A will ship 30, 60, 0, & 10 items to Warehouses 1-4 respectively.
Plant B will ship 50, 0, 70, & 0  items to Warehosues 1-4 respectively.

Since Warehouse 4 doesn't exist we will not be shipping those 10 items from PlantA

```{r}
get.objective(lprec)
get.variables(lprec)
```

